---
title: "Work Requirements Under Review: Impacts of SNAP Time Limits on Able-Bodied Adults without Dependents"
subtitle: "By Catria Gadwah-Meaden"
author: |
  Hussain Hadah<sup>1,2</sup>
  <br>
  <div style="text-align: center; font-size: 0.8em; margin-top: 10px;">
  <sup>1</sup>Economics Department, Tulane University, <sup>2</sup>The Murphy Institute
  </div>

date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "assets/tulane-fonts.css", "assets/tulane.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: false # show a title slide with YAML information
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' # alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: false # disable slide transitions by scrolling
---

class: title-slide

# Work Requirements Under Review: Impacts of SNAP Time Limits on Able-Bodied Adults without Dependents


.pull-left[
**Paper by: Catria Gadwah-Meaden**

**Discussant: Hussain Hadah**<sup>1,2</sup>

<div style="color: white; font-size: 18px; margin-top: 10px;">
`r format(Sys.time(), '%B %d, %Y')`
</div>

<div style="font-size: 0.8em; margin-top: 10px;">
<sup>1</sup>The Murphy Institute, Tulane University<br>
<sup>2</sup>Economics Department, Tulane University<br>
</div>
]

---
layout: true
<div style="position: absolute;left:20px;bottom:5px;color:black;font-size: 12px;">Hussain Hadah (Tulane/Murphy Institute)  | `r format(Sys.time(), '%d %B %Y')`</div>

<!--- `r rmarkdown::metadata$subtitle` | `r format(Sys.time(), '%d %B %Y')`-->

```{r, load_refs, echo=FALSE, cache=FALSE, message=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           cite.style = 'authoryear', 
           style = "markdown",
           hyperlink = FALSE, 
           dashed = FALSE)
myBib <- ReadBib("assets/example.bib", check = FALSE)
top_icon = function(x) {
  icons::icon_style(
    icons::fontawesome(x),
    position = "fixed", top = 10, right = 10
  )
}
```

```{r setup, include=FALSE}
# xaringanExtra::use_scribble() ## Draw on slides. Requires dev version of xaringanExtra.

options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=4, fig.width=6,
  out.width="748px", out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )
```


```{r, cache=FALSE, message=FALSE, warning=FALSE, include=TRUE, eval=TRUE, results=FALSE, echo=FALSE, tidy.opts = list(width.cutoff = 50), tidy = TRUE}
## Load and install the packages that we'll be using today
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tictoc, parallel, pbapply, future, future.apply, furrr, RhpcBLASctl, memoise, here, foreign, mfx, tidyverse, hrbrthemes, estimatr, ivreg, fixest, sandwich, lmtest, margins, vtable, broom, modelsummary, stargazer, fastDummies, recipes, dummy, gplots, haven, huxtable, kableExtra, gmodels, survey, gtsummary, data.table, tidyfast, dtplyr, microbenchmark, ggpubr, tibble, viridis, wesanderson, censReg, rstatix, srvyr, formatR, sysfonts, showtextdb, showtext, thematic, sampleSelection, RefManageR, DT, googleVis, png, grid)
# devtools::install_github("thomasp85/patchwork")
remotes::install_github("mitchelloharawild/icons")
remotes::install_github("ROpenSci/bibtex")

# devtools::install_github("ajdamico/lodown")
## My preferred ggplot2 plotting theme (optional)
## https://github.com/hrbrmstr/hrbrthemes
# scale_fill_ipsum()
# scale_color_ipsum()
font_add_google("Fira Sans", "firasans")
font_add_google("Fira Code", "firasans")

showtext_auto()

theme_customs <- theme(
  text = element_text(family = 'firasans', size = 16),
  plot.title.position = 'plot',
  plot.title = element_text(
    face = 'bold', 
    colour = thematic::okabe_ito(8)[6],
    margin = margin(t = 2, r = 0, b = 7, l = 0, unit = "mm")
  ),
)

colors <-  thematic::okabe_ito(5)

# theme_set(theme_minimal() + theme_customs)
theme_set(hrbrthemes::theme_ipsum() + theme_customs)
## Set master directory where all sub-directories are located
mdir <- "/Users/hhadah/Documents/GiT/urban-econ/slides/01-week1/tue"

## Set working directory

# COLOR PALLETES
library(paletteer) 
# paletteer_d("awtools::a_palette")
# paletteer_d("suffrager::CarolMan")

### COLOR BLIND PALLETES
#paletteer_d("colorblindr::OkabeIto")
#paletteer_d("colorblindr::OkabeIto_black")
# paletteer_d("colorBlindness::paletteMartin")
# paletteer_d("colorBlindness::Blue2DarkRed18Steps")
# paletteer_d("colorBlindness::SteppedSequential5Steps")
# paletteer_d("colorBlindness::PairedColor12Steps")
# paletteer_d("colorBlindness::ModifiedSpectralScheme11Steps")
colorBlindness <- paletteer_d("colorBlindness::Blue2Orange12Steps")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# scale_colour_paletteer_d("colorBlindness::ModifiedSpectralScheme11Steps", dynamic = FALSE)
# To use for fills, add
  scale_fill_manual(values="colorBlindness::Blue2Orange12Steps")

# To use for line and point colors, add
  scale_colour_manual(values="colorBlindness::Blue2Orange12Steps")
  #<a><button>[Click me](#sources)</button></a>
```

```{css, echo=F}
    /* Table width = 100% max-width */

    .remark-slide table{
        width: auto !important; /* Adjusts table width */
    }

    /* Change the background color to white for shaded rows (even rows) */

    .remark-slide thead, .remark-slide tr:nth-child(2n) {
        background-color: white;
    }
    .remark-slide thead, .remark-slide tr:nth-child(n) {
        background-color: white;
    }
```

---
## Research Questions


### How do work requirements for SNAP recipients affect able-bodied adults without dependents (ABAWDs)?
<br>

### How do work requirements for SNAP recipients affect the employment outcomes of ABAWDs?
<br>


### The paper uses the staggered take-up of work requirements after the great recession as a .brand-crawfest[policy variation]

---
## Method and Results

### Uses .brand-crawfest[difference-in-differences (DiD)] to estimate the causal effect of work requirements

  - Uses Callaway & Sant’Anna (2021) 

<br>

### The adoption of work requirements led to a:

<ol>
  <li><h4>11% decrease in SNAP participation</h4></li>
  <li><h4>No effect on employment outcomes</h4></li>
</ol>

---
## Questions for the Author

1. What do you mean that you fail to find of work requirements on employment outcomes that are not attenuated by the inclusion of covariates?
2. Using Callaway & Sant’Anna (2021) forces you to assign dichotomous treatment status---prevents you from using the county to PUMA treatment assignment used in the literature. Did you try to use a continuous treatment variable using other DiD methods?

---
## Suggestions

### Showing the DiD results before conditional parallel trends assumption is, in my opinion, important for transparency
<br>

### To prevent confusion, I suggest explaining in details the policy variation as a result of the three-month 10 percent unemployment rate cutoff to individual counties during the Great Recession
<br>

### You mention that DDD to take advantage of additional conditions to identify a more robust causal effect. Not having a package to do the estimation is not a valid reason to not use DDD. 



```{r gen_pdf, include = FALSE, cache = FALSE, eval = TRUE}
library(renderthis)
# https://hhadah.github.io/appam-discussant-slides/catria/catria.html

to_pdf(from = "~/Documents/GiT/appam-discussant-slides/catria/catria.html", 
       to = "~/Documents/GiT/appam-discussant-slides/catria/catria.pdf")
to_pdf(from = "~/Documents/GiT/appam-discussant-slides/catria/catria.html")
```
